\begin{enumerate} %[label=(E\arabic*).]

\item 
\textbf{Course Coordinator}, One-Week Faculty Development Program on \textit{IoT, What and How?}, December 24 – 28, 2018 (EICT Aacdemy, IIT Roorkee).
\item 
\textbf{Course Coordinator}, One-Week Faculty Development Program on \textit{High Performance Computing and Deep Learning}, October 21-25, 2018 (EICT Aacdemy, IIT Roorkee).
\item
\textbf{Course Coordinator}, One-Week Faculty Development Program on \textit{Internet of Things}, January 13-17, 2018 (EICT Academy, IIT Roorkee)

\item
\textbf{Course Coordinator}, One-Week Short Course on \textit{Recent Trends in Network Security}, January 8-12, 2018 (ISEA Project, Phase-II \& EICT Academy, IIT Roorkee) (Invited 3 international speakers)

\item
\textbf{Course Coordinator}, Two-weeks Faculty Development Program on \textit{Computer Networks and Security}, May 24th - June 2nd, 2017 (EICT Academy, IIT Roorkee)

\item
\textbf{Course Coordinator}, One-week Short Course on \textit{Recent Trends in Network Security}, December 14-18, 2016 (ISEA Project, Phase-II)

\item
\textbf{Course Coordinator}, One-week Short Course on \textit{Recent Trends in Network Security}, February 1-5, 2016. (ISEA Project, Phase-II)

\item
\textbf{Organizing Committee Member (CSE)}, Conference on \textit{Recent Advances in Electronics and Computer Engineering (RAECE)}, IIT Roorkee, February 14-15, 2015.

\item
\textbf{Faculty Coordinator}, \textit{Code.fun.do – 24-hour hackathon, Microsoft, ACM IITR Students Chapter}, Dept. of CSE, February 6-8, 2015

\item
\textbf{Faculty Coordinator}, ACM one-day workshop on “\textit{Business Process Simulation}”, (17th January, 2015), Prof. D.S. Broca, XLRI, Jhamshedpur

\item
\textbf{Faculty Coordinator}, ACM inaugural lecture on “\textit{Emerging Trends in Cloud Computing}” (12th April 2014), Prof. Janakiram D, IIT Madras 

\item
\textbf{Faculty Coordinator}, Asian Programming Contest – 2014 (29th March, 2014)

\item
\textbf{Convener}, QIP Short Term Course on “\textit{Developments and Challenges in Cloud Computing}” (10-14 June, 2013)

\item
\textbf{Convener}, One-day workshop on\textit{ High Performance Computing}. June, 2012

\item
\textbf{Organizing Member}, Two-day workshop on\textit{ Cloud Computing and Security Issues}, 12-13 July, 2012, Osmania University, Hyderabad, India.

\item
\textbf{Convener}, National Level Students Technical Symposium (Paper Presentation Competition) , “ABHISARGA-2004” (23rd – 24th Sept., 2004) 

\item
\textbf{Convener}, National Short Term Training Program on OOAD \& UML(18th – 22nd July, 2005) 

\item
\textbf{Convener}, National Short Term Training on Databases \& Oracle (9th – 13th March, 2006) 

\item
\textbf{Convener}, State Level Competitions for INFOSYS campus connect students, ASPIRATIONS-2020 (14th August, 2007) 

\item
\textbf{Convener}, Second Alumni Meet (23rd February, 2008) 

\item
\textbf{Acted as Chairperson}, Advisor or Member for various events organized at National level or State level.

\end{enumerate}