\begin{itemize}
\item[(A)]  Awards and Professional Recognitions:

\begin{itemize}
	\item[\#]
	Recipient of the \emph{\textbf{Merit Scholarship for University 4th Rank}}
	in Master's Course (1995).
	
	\item[\#]
	Recipient of the \emph{\textbf{Travel Grants from Department of Science and Technology, Ministry of S \& T}}
	(INR 1.8 Lakhs).
	
	\item[\#]
	Recipient of the \emph{\textbf{Best Paper Award}} (Conference).
	
	\item[\#]
	Recipient of the \emph{\textbf{Best Presentation Award}} (Conference).

	\item[\#]
	Recipient of \textbf{\textit{IBM Shared University Award}} (from September 2013 to September 2016)
\end{itemize}

\item[(B)] Other Significant Accomplishments for Professional Recognition: 

\begin{itemize}
	\item[*] Editor, Journal of Spatio-Temporal Data Science, Inderscience.

	\item[*] Vice Chairman, IEEE Computer Society, India Council (2015-Till Date).

	\item[*] Secretary, IEEE Roorkee Subsection, India (2018-Till Date).

	\item[*] Founder Faculty Sponsor, ACM Students Chapter, IIT Roorkee, India (2015-Till Date).
	
	\item[*] Chaired Session in IEEE MASS 2017, flagship conference in MANETs and Sensors.
		
	\item[*] Reviewer: IEEE Trans. Cloud Computing
	
	\item[*] Reviewer: IEEE Trans. Service Computing
	
	\item[*] Outstanding Reviewer: Elsevier Computer Networks

	\item[*] Recognized Reviewer: Elsevier Computers and Security

	\item[*] Reviewer: Elsevier Journal of Network and Computer Applications
	
	\item[*] Reviewer: Springer International Journal of Information Security
	
	
	\end{itemize}
		\end{itemize}