
\begin{enumerate}


\item
\textbf{Program Committee Member}, \textit{IEEE International Symposium on Smart Electronic Systems} \textbf{(iSES 2018)}. Track - Hardware/Software for Internet of Things and Consumer Electronics , December 17-19, 2018, Hyderabad, India.

\item
\textbf{Workshop Co-Chair}, \textit{The Fifth International Conference on Internet of Things - Systems, Management and Security} \textbf{(IoTSMS 2018)} , October 15-18, 2018, Valencia, Spain.

\textbf{Program Committee Member}, \textit{The 15th IEEE International Conference on Advanced and Trusted Computing} \textbf{(IEEE ATC 2018)} , October 8-12, 2018, Guangzhou, China

\item
\textbf{Program Committee Member}, \textit{The 2nd IEEE International Workshop on 5G in Internet of Things} \textbf{(5G-IoT 2018)} as part of \textit{The 43rd IEEE Conference on Local Computer Networks} \textbf{(LCN)} , October 1-4, 2018, Chicago, USA

\item
\textbf{General Chair}, \textit{IEEE International Workshop on Smart Living with IoT, Cloud, and Edge Computing }(\textbf{SLICE 2018}), in conjunction with The \textit{Third IEEE International Conference on Fog and Mobile Edge Computing} (\textbf{FMEC 2018}), April 23-26, 2018, Barcelona, Spain

\textbf{Program Committee Member}, \textit{International Conference on Innovative Technologies in Engineering} \textbf{(ICITE 2018) }, April 11-13, 2018, Hyderabad, India

\item
\textbf{Publication and EDAS Co-Chair}, \textit{The Six IEEE International Workshop on Cloud Computing Systems, Networks, and Applications }(\textbf{CCSNA}) in conjunction with \textit{IEEE Mobile Adhoc and Sensor Systems} (\textbf{MASS 2017}), October 22-25, 2017, Orlando, FL, USA.

\item
\textbf{Program Committee Member}, \textit{The 14th IEEE Conference on Advanced and Trusted Computing} (\textbf{ATC-2017}), August 4-8, 2017, San Francisco Bay Area, USA.

\item
\textbf{Program Committee Member}, \textit{First International Workshop on Artificially Intelligent Smart SocieTies} (\textbf{AIST2017}), \textit{3rd IEEE International Conference on Smart Computing} (\textbf{SMARTCOMP 2017}), May 29-31, 2017, Hong Kong.

\item
\textbf{Program Committee Member},\textit{ Hardware/Software for Internet of Things and Consumer Electronics Track in 3rd IEEE International Symposium on Nanoelectronic and Information Systems} (\textbf{IEEE-iNIS}), 18-20 December, 2017, Bhopal, India.

\item
\textbf{Program Committee Member}, \textit{2018 8th International Conference on Cloud Computing, Data Science \& Engineering- Confluence 2018}, January 11-12, 2018, Noida, India.

\item
\textbf{Program Committee Member}, \textit{Asia Security and Privacy Conference 2017} (\textbf{Asia S\&P 2017}), Jan 30th - Feb 1st, 2017, SVNIT Surat, India.

\item
\textbf{Program Committee Member},  \textit{Confluence-2016: GLOBAL Technology, Innovation \& Entrepreneurship Summit 2016 }(\textbf{Global TIE Summit 2016}),\textit{ 6th International Conference on Cloud System and Big Data Engineering, Confluence}, 14-15, January, 2016, Noida, Delhi-NCR, India

\item
\textbf{Program Committee Member},  \textit{Fifth International Conference on Communication Systems and Network Technologies }(\textbf{CSNT}), 4-6, April, 2015, Gwalior, India

\item
\textbf{Program Committee Member}, \textit{IEEE 14th International Conference on Information Technology} (\textbf{ICIT}), 21-23, December, 2015, Bhubaneshwar, India

\item
\textbf{Technical Program Committee Member}, \textit{IEEE Region 10 Technical Symposium 2015} (\textbf{TENSYMP}), 13-15, May, 2015, Ahmedabad, Gujarat, India

\item
\textbf{Technical Program Committee Member}, \textit{Fifth International Conference on Communication Systems and Network Technologies} (\textbf{CSNT}), 4-6, April, 2015, Gwalior, India.

\item
\textbf{Session Chair}, \textit{International Conference on Computing and Communication Technologies} (\textbf{ICCCT}), 11-13, December, 2014, Dept. of CSE, Osmania University, Hyderabad (Held at Novotel Hotel), India

\item
\textbf{Technical Program Committee Member}, \textit{International Conference on Computing and Communication Technologies }(\textbf{ICCCT}), 11-13, December, 2014, Dept. of CSE, Osmania University, Hyderabad, India

\item
\textbf{Program Committee member of Communication Networks and Protocols}, \textit{13th International Conference on Information Technology} (\textbf{ICIT}), 22-24, December, 2014, Bhuvaneshwar, India

\item
\textbf{Track Chair}, \textit{Multimedia Communication Systems and Networks }(\textbf{MCSN}) track of the \textit{2nd International Conference on Telecommunication Systems and Networks - MIC-Telecom 2014}, Istanbul, Turkey, 19-21 December 2014 

\item
\textbf{Track Chair}, \textit{Online Learning and Education} (\textbf{OLE}) track of the \textit{1st International Conference on Communications and Computer Networks - MIC-Networks 2014}, Dubai, UAE, 7-9 February 2014

\item
\textbf{Program Committee Member}, \textit{5th International Conference Confluence 2014 The Next Generation Information Technology Summit} (\textbf{Confluence-2014}), 25-26, September, 2014, Amity University, Noida, U.P., India

\item
\textbf{Technical Program Committee Member}, \textit{Green Computing and Communication Track, 2nd International Conference on Computer Science and Engineering} (\textbf{MIC-Computing 2014}), 15-17, August, 2014, Milan, Italy.

\item
\textbf{Technical Program Committee Member},\textit{ Second International Symposium on Security in Computing and Communications} (\textbf{SSCC’14}), 24-27, September, 2014, Galgotias Educational Institutions, Greater Noida, India

\item
\textbf{Technical Program Committee Member}, \textit{4th International Conference on Advances in Computing, Communications and Informatics}, 10-13, August, 2014, Kochi, Kerala, India.

\item
\textbf{Session Chair}, \textit{IEEE International Conference on Security and Reliability} (\textbf{SERE}) held during 18-20 June, 2013 at\textit{ National Institute of Science and Technology} (\textbf{NIST}), Gaithersburg, Washington DC, USA

\item
\textbf{Advisory Board Member}, \textit{National Conference on National conference on Advances in Computing, Networking and Security} to be held during 23rd and 24th December 2013, Sri Guru GovindSinghji Institute of Engineering and Technology, Nanded, Maharastra, India

\item
\textbf{Advisory Board Member}, \textit{National Conference on Wireless Communication and Embedded Systems} (\textbf{NCWCE – 2013}) held on 23, February 2013, at Department of Electronics and Communications Engineering, Jayalaxmi Institute of Technology, Dharmapuri, Tamilnadu. 

\item
\textbf{Technical Program Committee}, \textit{Mosharaka International Conference, Green Computing and Communications} (\textbf{GCC}), MIC-CAI2013, 5-7 April 2013, Belgrade, Serbia.

\item
\textbf{Technical Program Committee}, \textit{Mosharaka International Conference, Web and Internet Technologies} (\textbf{WIT}), MIC-CSP2013, 5-7 April 2013, Belgrade, Serbia.

\item
\textbf{Advisory Board Member}, \textit{National Conference on Emerging Technologies in Computer Science}  (\textbf{ETCS-12})  held during 20-21, October, 2012 at Department of CSE, IT and MCA, Noida Institute of Engineering and Technology (NIET), Greater Noida, India.

\item
\textbf{Technical Program Committee}, \textit{Mosharaka International Conference, Cloud, Grid and Internet Computing} (\textbf{CGIC}), MIC-CCA2012, 12-14 October 2012, Istanbul, Turkey.

\item
\textbf{Technical Program Committee}, \textit{Mosharaka International Conference, Green Computing and Communications} (\textbf{GCC}), MIC-CAI2012, 15-17 June 2012, Palma de Mallorca, Spain.

\item
\textbf{Technical Program Committee},\textit{ Mosharaka International Conference, Parallel and Distributed Computing} (\textbf{PDC}), MIC-CAI2012, 15-17 June 2012, Palma de Mallorca, Spain.

\item
\textbf{Technical Program Committee},\textit{ Mosharaka International Conference, Mobile Computing and Applications} (\textbf{MCA}), MIC-WCMC2012, 15-17 June 2012,  Palma de Mallorca, Spain.

\item
\textbf{Session Chair},\textit{ Joint UACEE International Conference on Pervasive Computing and Communications} (\textbf{PCC 2012}) and \textit{Second International Conference on Computing, Control and Communication }(\textbf{CCN-2012}), 17th June, 2012, NCR-Delhi, India

\item
\textbf{Organizing Committee}, \textit{National Workshop on Cloud Computing and Security Issues}, 12th -13th July, 2012, Department of CSE, Osmania University, Hyderabad, India

\item
\textbf{Session Chair}, \textit{The 2012 FTRA International Conference on Advanced IT, engineering Management for Industrial Technology} (\textbf{FTRA AIM 2012}), February 6-8, Hana Square, Korea University, Seoul, Korea.

\item
\textbf{Technical Program Committee}, \textit{Green Computing and Communications} (\textbf{GCC}) track of \textit{Mosharaka International Conference on Computing and Artificial Intelligence} (\textbf{MIC-CAI2012}), Palma de Mallorca, Spain: 15-17 June 2012. 

\item
\textbf{Program Committee}, \textit{IEEE International Conference on Communication Systems and Network Technologies} (\textbf{CSNT-2012}), (10th – 14th May, 2012), Rajkot, India.

\item
\textbf{Technical Program Committee}, \textit{Mosharaka International Conference, Mesh, Ad Hoc and Sensor Networks} (\textbf{MAS}), MIC-CES2011, 16-18 December 2011, Dubai, UAE.

\item
\textbf{Program Committee}, \textit{International Conference on Computational Intelligence and Communication Networks }(\textbf{CICN 2011}), (7th – 9th October, 2011) Gwalior, India

\item
\textbf{Technical Program Committee}, \textit{Mosharaka International Conference, Mobile Computing and Applications} (\textbf{MCA}), MIC-WCMC2011, 3-5 June 2011, Istanbul, Turkey.

\item
\textbf{Advisory and Technical Committee}, \textit{Advanced Computing Research Society.}

\item
\textbf{Technical Program Committee}, \textit{major IACSIT Conferences}.

\item
\textbf{Technical Program Committee}, \textit{major Mosharaka Conferences}.

\item
\textbf{Technical Program Committee}, \textit{Second Vaagdevi IEEE Conference on IT for Real World Problems} (9th – 11th December, 2010), Warangal, India

\item
\textbf{Technical Program Committee}, \textit{Communications and Computer Networks} (\textbf{CCN}) track and \textit{Communication and Information Technology} (\textbf{CIT}) track of\textit{ Mosharaka IEEE International Conference on Communications, Networking and Information Technology} (\textbf{MIC-CNIT2010}) (December, 2011), Amman, Jordan.

\item
\textbf{Technical Program Committee}, \textit{Mosharaka IEEE International Conference on Communications, Computers and Applications} (Nov, 2011), Amman, Jordan.

\item
\textbf{Technical Program Committee}, \textit{Communications and Computer Networks} (\textbf{CCN}) track and \textit{Communication and Information Technology} (\textbf{CIT}) track of \textit{Mosharaka IEEE International Conference on Communications, Networking and Information Technology} (\textbf{MIC-CNIT2010}) (3rd – 5th, December, 2010), Amman, Jordan.

\item
\textbf{Technical Program Committee}, \textit{Mosharaka IEEE International Conference on Communications, Computers and Applications} (26th – 28th October, 2009), Amman, Jordan.

\item
\textbf{General Chair}, \textit{IEEE International Conference on Software Technology and Engineering} (27th – 29th Jun, 2009), Chennai, India.

\item 
\textbf{Program Committee},\textit{ IEEE International Conference on Advanced Computing on Theory and Engineering} (\textbf{ICACTE}) (20th – 22nd Dec, 2008), Pukhet, Thailand. 

\item
\textbf{General Chair / Program Committee for many International Conferences} (\textbf{including IEEE}) organized by IACSIT, Singapore.

\end{enumerate}