\begin{enumerate}[label=(C\arabic*).]	

	\item
	A. Anshul, \textbf{Sateesh K. Peddoju}, \lq\lq \textit{NTPDroid: A Hybrid Android Malware Detector using Network Traffic and System Permissions},\rq\rq\, in 2018 IEEE Trustcom/BigDataSE, New York, 2018, "Accepted" (ERA/CORE Rank: \textbf{A})
	
	\item
	M. Santra, \textbf{Sateesh K. Peddoju}, A. K. Bhattacharjee, and A. Khan, \lq\lq \textit{Design and Analysis of a Modified Remote Attestation Protocol},\rq\rq\, in 2017 IEEE Trustcom/BigDataSE/ICESS, Sydney, 2017, pp. pp. 578-585. (ERA/CORE Rank: \textbf{A})
	
	\item
	A. Ravi and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Energy-Service Trade-Off Model for Mobile Cloud Computing},\rq\rq\, in 2017 IEEE 14th International Conference on Mobile Ad Hoc and Sensor Systems (MASS), 2017, pp. 616-621. (ERA/CORE Rank: \textbf{B}).
	
	\item
	V. Mahajan and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Deployment of Intrusion Detection System in Cloud: A Performance-Based Study},\rq\rq\,  in Trustcom/BigDataSE/ICESS, 2017 IEEE, 2017, pp. 1103-1108. (ERA/CORE Rank: \textbf{A}).
	
	\item
	A. Kuity and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Performance Evaluation of Container-Based High Performance Computing Ecosystem Using OpenPOWER},\rq\rq\,  in International Conference on High Performance Computing, 2017, pp. 290-308. (ERA/CORE Rank: \textbf{B}).
	
	\item
	A. Chaudhary, \textbf{Sateesh K. Peddoju}, and K. Kadarla, \lq\lq \textit{Study of Internet-of-Things Messaging Protocols Used for Exchanging Data with External Sources},\rq\rq\,in 2017 IEEE 14th International Conference on Mobile Ad Hoc and Sensor Systems (MASS), 2017, pp. 666-671. (ERA/CORE Rank: \textbf{B}).
	
	\item
	A. Arora and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Minimizing Network Traffic Features for Android Mobile Malware Detection},\rq\rq\, in Proceedings of the 18th International Conference on Distributed Computing and Networking, 2017, p. 32. (ERA/CORE Rank: \textbf{B}).
	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Mask Region Grow segmentation algorithm for low-computing devices},\rq\rq\, in Communication (NCC), 2016 Twenty Second National Conference on, 2016, pp. 1-6. (ERA/CORE Rank: \textbf{B}).
	
	\item
	P. Deshpande, S. Sharma, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Data Storage Security in Cloud Paradigm},\rq\rq\, in Proceedings of Fifth International Conference on Soft Computing for Problem Solving, 2016, pp. 247-259.  \textit{(IIT Roorkee)}.
	
	\item
	A. Sharma and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Response time based load balancing in cloud computing},\rq\rq in Control, Instrumentation, Communication and Computational Technologies (ICCICCT), 2014 International Conference on, 2014, pp. 1287-1293.
	
	\item
	A. Ravi and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Mobility managed energy efficient Android mobile devices using cloudlet},\rq\rq\, in Students' Technology Symposium (TechSym), 2014 IEEE, 2014, pp. 402-407.\textbf{ \textit{(IIT Kharagpur)} (Best Presentation Award)}.
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Mobile Mixed Reality Based Damage Level Estimation of Diseased Plant Leaf},\rq\rq\, in Next Generation Mobile Apps, Services and Technologies (NGMAST), 2014 Eighth International Conference on, 2014, pp. 72-77.
	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Energy efficient mobile vision system for plant leaf disease identification},\rq\rq\, in Wireless Communications and Networking Conference (WCNC), 2014 IEEE, 2014, pp. 3314-3319. (ERA/CORE Rank: \textbf{B}).
	
	\item
	M. H. Kumar and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Energy efficient task scheduling for parallel workflows in cloud environment},\rq\rq\, in Control, Instrumentation, Communication and Computational Technologies (ICCICCT), 2014 International Conference on, 2014, pp. 1298-1303.
	
	\item
	G. Garkoti, \textbf{Sateesh K. Peddoju}, and R. Balasubramanian, \lq\lq \textit{Detection of insider attacks in cloud based e-healthcare environment},\rq\rq\, in Information Technology (ICIT), 2014 International Conference on, 2014, pp. 195-200.
	
	\item
	S. Garg, A. K. Sarje, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Improved detection of P2P botnets through network behavior analysis},\rq\rq\, in International Conference on Security in Computer Networks and Distributed Systems, 2014, pp. 334-345.
	
	\item
	S. Garg, A. Sarje, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Network traffic analysis of zeroaccess bot},\rq\rq\, in The ASE International conference on Cyber Security, Stanford University, 2014.
	
	\item
	P. Deshpande, S. Sharma, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Implementation of a private cloud: a case study},\rq\rq\, in Proceedings of the Third International Conference on Soft Computing for Problem Solving, 2014, pp. 635-647.
	
	\item
	A. Arora, S. Garg, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Malware detection using network traffic analysis in android based mobile devices},\rq\rq\,in Next generation mobile apps, services and technologies (NGMAST), 2014 eighth international conference on, 2014, pp. 66-71.
	
	\item
	T. Sen and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Hierarchal identity based socket for datacenters},\rq\rq\, in Software Security and Reliability-Companion (SERE-C), 2013 IEEE 7th International Conference on, 2013, pp. 63-67.
	
	\item
	A. Ravi and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Energy efficient seamless service provisioning in mobile cloud computing},\rq\rq\, in Service Oriented System Engineering (SOSE), 2013 IEEE 7th International Symposium on, 2013, pp. 463-471.
	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Mobile plant species classification: a low computational approach},\rq\rq\, in Image Information Processing (ICIIP), 2013 IEEE Second International Conference on, 2013, pp. 405-409.
	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Unsupervised resolution independent based natural plant leaf disease segmentation approach for mobile devices},\rq\rq\, in Proceedings of the 5th IBM Collaborative Academia Research Exchange Workshop, 2013, p. 11.
	
	\item
	S. Prasad, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Mobile augmented reality based interactive teaching \& learning system with low computation approach},\rq\rq\, in Computational Intelligence in Control and Automation (CICA), 2013 IEEE Symposium on, 2013, pp. 97-103.
	
	\item
	A. Mehta, S. Prasad, and  \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Improved Connected Region Based Approach for Extraction of Principal Lines from Palm Images},\rq\rq\, in Proceedings of Elsevier International Conference of Image and Signal Processing, 2013, pp. 104-111. \textbf{(Best Paper Award)}
	
	\item
	A. Jain, M. Mishra, \textbf{Sateesh K. Peddoju}, and N. Jain, \lq\lq \textit{Energy efficient computing-green cloud computing},\rq\rq\, in Energy Efficient Technologies for Sustainability (ICEETS), 2013 International Conference on, 2013, pp. 978-982.
	
	\item
	S. Garg, A. K. Singh, A. K. Sarje, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Behaviour analysis of machine learning algorithms for detecting P2P botnets},\rq\rq\, in Advanced computing technologies (ICACT), 2013 15th international conference on, 2013, pp. 1-4.
	
	\item
	P. Deshpande, S. Sharma, and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Deploying a private cloud? Go through the errors first},\rq\rq\, in Conference on Communication and Control Systems(CACCS-2013)-2013, Deharadun-India, 2013.
	
	
	\item
	V. Chouhan and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Hierarchical storage technique for maintaining hop-count to prevent ddos attack in cloud computing},\rq\rq\, in Proceedings of International Conference on Advances in Computing, 2013, pp. 511-518.
	
	\item
	H. Verma, D. Toshniwal, and  \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Distributed frequent itemset mining framework for incremental data using MPI-style WSRF services},\rq\rq\,in Proceedings of the International Conference on Advances in Computing, Communications and Informatics, 2012, pp. 74-81.
	
	\item
	S. Prasad, A. Prakash, \textbf{Sateesh K. Peddoju}, and D. Ghosh, \lq\lq \textit{Control of computer process using image processing and computer vision for low-processing devices},\rq\rq\, in Proceedings of the International Conference on Advances in Computing, Communications and Informatics, 2012, pp. 1169-1174.
	
	\item
	A. Kuity and \textbf{Sateesh K. Peddoju}, \lq\lq \textit{Advanced Reservation based SLA for Resource negotiations in Grid Scheduling},\rq\rq\,in Proc. of the Intl. Conf. on Advances in Computer, Electronics and Electrical Engineering, 2012.
	
	\end{enumerate}