\begin{enumerate} [label=(T\arabic*).]

\item
\textbf{Invited Talk:} Delivered a Guest Talk on "\textit{Energy Efficiency and Seamless Service Provisioning in Mobile Cloud Computing}", on 19th October, 2017 at University at Albany, State University of New York (SUNY), USA. 

\item
\textbf{Invited Talk and Chief Guest:} "\textit{Parallel Computing Performance and Big Data Programming}", on 20th February 2016 at FDP on Parallel Computing, Feb 11-20, 2016, National Institute of Technology, Warangal.

\item
\textbf{Tutorial Session}, “\textit{IoT and Cloud}”, National Conference on Big Data Analytics \& Cloud Computing, Department of CSE, University College of Engineering(A), 29-31 December 2015, Osmania University, Hyderabad.

\item
\textbf{Chief Guest and Keynote Speaker}, “\textit{Mobile \& Cloud Computing}”, ASTRA-2k15, 27th \& 28th November 2015, Vaagdevi College of Engineering, Warangal.

\item
\textbf{Invited Speaker}, “\textit{Cloud Computing and its Research}”, Two-day workshop on Cloud Computing, TEQIP-II, 27-28, October, 2015, Government Engineering College, Bikaner, Rajasthan.

\item
\textbf{Invited Speaker}, “\textit{Attack Scenarios in Cloud Computing}”, Symposium on Cloud Computing and Digital Forensics, 4th September, 2015, BITS Pilani University, Hyderabad Campus.

\item
\textbf{Chief Guest and Chairperson of a Technical Session} and Plenary Session on “\textit{Cloud Computing Research}” of International Conference on Science and Technology 2015 for its conference track "Computer Science” February 27-28, 2015 organized by SRMS College of Engineering and Technology Bareilly, UP

\item
\textbf{Tutorial Session}, “\textit{Researching Cloud Computing using Cloudsim}”, International Conference on Computing and Communication Technologies (ICCCT), 11-13, December, 2014, Dept. of CSE, Osmania University, Hyderabad, India

\item
\textbf{Invited Speaker}, “\textit{Cloudsim}”, 11 October, 2014, GurukulKangri University, Haridwar, India.

\item
\textbf{Speaker for various sessions} on topics like “\textit{Fundamentals}”, “\textit{Virtualization}”, “\textit{Advances}”, “\textit{Mobile Cloud}” during the self-organized program, QIP Short Term Course on “\textit{Developments and Challenges in Cloud Computing}”, 10-14 June, 2013, Department of CSE and QIP Center, IIT Roorkee.

\item
\textbf{Invited Speaker}, “\textit{Opportunities and Challenges in Wireless Sensor Networks}” (21st March, 2013), AICTE Faculty Development Program on “\textit{Wireless Sensor Networks}”, 18-22 March, 2013, Sri Guru GovindSinghji Institute of Engineering and Technology, Nanded, Maharastra, India.

\item
\textbf{Guest of Honor and Keynote Speaker}, “\textit{Recent Trends in Cloud Computing}” (20th March, 2013), AICTE Faculty Development Program on “\textit{Cloud Computing and its Applications}”, 20-24, Mar, 2013, PDA College of Engineering, Gulbarga, Karnataka, India

\item
\textbf{Guest of Honor and Invited Speaker}, “\textit{Demonstration of Cloud Computing Models}” (20th March, 2013), AICTE Faculty Development Program on “\textit{Cloud Computing and its Applications}”, 20-24, Mar, 2013, PDA College of Engineering, Gulbarga, Karnataka, India

\item
\textbf{Keynote Speaker}, “\textit{Importance of Simulations in Networking}”(15th February, 2013), Faculty Development Program on ” \textit{Network Simulator NS-2}″ , AKG Engineering College, Ghaziabad, Delhi NCR, India

\item
\textbf{Invited Speaker}, “\textit{Wireless Simulations in NS – 2}″ (15th February, 2013), Faculty Development Program on ” \textit{Network Simulator NS-2}″ , AKG Engineering College, Ghaziabad, Delhi NCR, India

\item
\textbf{Invited Speaker}, “\textit{Demonstration of Wireless environment using NS-2}″ (16th February, 2013), Faculty Development Program on ” \textit{Network Simulator NS-2}″ , AKG Engineering College, Ghaziabad, Delhi NCR, India

\item
\textbf{Invited Speaker}, “\textit{Results, Analysis, and Graphs of Wireless environment using NS-2}″ (16th February, 2013), Faculty Development Program on ” \textit{Network Simulator NS-2}″ , AKG Engineering College, Ghaziabad, Delhi NCR, India

\item
\textbf{Invited Speaker}, “\textit{Advances in IRS – Extensions to Cloud Computing}” (28th January, 2013), DST Workshop on “\textit{Information Retrieval Systems}”, 28-29, January, 2013, Varadha Reddy Engineering College, Warangal, A.P., India.

\item
\textbf{Chief Guest and Invited Speaker}, “\textit{Recent Trends in Mobile Cloud Computing}”, Workshop on Recent Trends in Cloud Computing, 3-4, August, 2012, KPR Institute of Technology, Coimbatore, Tamil Nadu, India.

\item
\textbf{Chief Guest and Keynote Speaker}, “\textit{Mobile Cloud Computing – Advances and Challenges}”, Joint UACEE International Conference on Pervasive Computing and Communications (PCC 2012) and Second International Conference on Computing, Control and Communication (CCN-2012), 17th June, 2012, NCR-Delhi, India

\item
\textbf{Invited Speaker}, “\textit{Wireless Networks and NS-2}” (2nd June, 2012), Workshop on Simulation Software/Tools, 1st – 2nd June, 2012, Noida Institute of Engineering and Technology, NCR-Delhi, India

\item
\textbf{Invited Speaker}, “\textit{MANETs and NS-2}” (26th February, 2012), Workshop on NS-2 held during 25th – 26th February, 2012, Graphic Era University, Dehradun, U.K., India.

\item
\textbf{Chief Guest and Keynote Speaker}, “\textit{Recent Advances in Mobile Communications}” (23rd Sept, 2011), National Symposium, SCINTELLACE 2k11. 23-24, Sept, 2011, JNT University, Cuddapah, India.

\item
\textbf{Invited Speaker}, “\textit{Mobile Ad-hoc Networks}” (6th June, 2008), National Workshop on Mobile Computing held during 5th – 7th June, 2008, Dept. of CSE, Osmania University, Hyderabad, India.

\item
\textbf{Invited Speaker}, “\textit{Object Oriented Programming}” (9th February, 2008), National Short-Term Training Program on “UML \& Automata” held during   9-11, February, 2008, KITS, Singapur, Karimnagar, India.

\item
\textbf{Invited Speaker}, “\textit{Simulations using NS-2}” (9th January, 2008), Pre-workshop tutorial in National Workshop for Research Scholars on “Mobile Ad hoc Networks: Issues and Challenges” held during 10th – 11th January, 2008, Dept. of CSE, Osmania University, Hyderabad, India.

\item
\textbf{Invited Speaker and Guest of Honor}, “\textit{NS-2 Simulator}” (30th June, 2007),  One-day National Seminar on “\textit{Network Simulation using OPNET and NS-2}” held on 30th June, 2007, Dept. of CSE, V.R. Siddhartha Engineering College, Vijayawada, India.

\item
\textbf{Invited Speaker}, “\textit{Mobile Ad-hoc Networks – Overview}” (23rd June, 2007),  Three-day National Seminar on “\textit{Networks \& Security}” held during 21st – 23rd June, 2007, Dept. of CSE, Srinidhi Institute of Science \& Technology, Ghatkesar, Hyderabad, India.

\item
\textbf{Guest of Honor and Invited Speaker}, “\textit{MANET Simulators}” (24th November, 2006), National Seminar on “\textit{Mobile \& Pervasive Computing}” during 24th – 25th Nov.,2006, PDA College of Technology, Gulburga, Karnataka, India.

\item
\textbf{Invited Speaker}, “\textit{Mobile Communications and NS-2}” (30th June – 1st  July , 2005), Three weeks National Refresher Course on Advanced Mobile Computing, Academic Staff College, J.N.T.U., Hyderabad.

\item
\textbf{Invited Speaker}, “\textit{NS-2 Demo}” (18th – 19th December, 2004), Three weeks National Refresher Course on Mobile Computing, Academic Staff College, J.N.T.U., Hyderabad, India.

\item
\textbf{Guest Lecture}, “\textit{Problem Solving Techniques}” (Oct, 2010 – Till date), Foundation Program (FP), INFOSYS Campus Connect (CC) at IEG – JKC, Vaagdevi College of Engineering, Warangal, India.

\item
\textbf{Guest Lecture}, “\textit{Web Technologies}” (Nov, 2008 – Jan, 2009), FP, INFOSYS CC at IEG – JKC, Vaagdevi College of Engineering, Warangal, India.

\item
\textbf{Guest Lecture}, “\textit{Programming Fundamentals}” (Aug, 2008, Oct, 2008), FP, INFOSYS CC at IEG – JKC, Vaagdevi College of Engineering, Warangal, India.

\item
\textbf{Guest Lecture}, “\textit{Programming Fundamentals}” (Jun, 2006, Apr, 2006, Jan, 2006), FP, INFOSYS CC at IEG – JKC,  KITS, Singapur, Karimnagar, India.



\end{enumerate}